\documentclass[12p,paper=a4]{jlreq}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\pagestyle{empty}

\setlength{\parindent}{0pt}

\makeatletter
\renewcommand{\section}{%
    \@startsection{section}{1}{\z@}%
    {24pt}%
    {6pt}%
    {\fontsize{19pt}{0pt}\selectfont\textbf}%
}
\makeatother

\begin{document}

\begin{center}
    \LARGE{\textbf{Hoshito Tajima}}
\end{center}
\begin{center}
    \textrm{Address: 2945-8 Shimoyoshida, Chichibu-shi, Saitama, Japan 369-1503}
\end{center}
\begin{center}
    \textrm{Phone Number: 080-9664-1149}
\end{center}
\begin{center}
    \textrm{E-mail: hoshito1022@gmail.com}
\end{center}

\hrulefill

\section*{Objective}

\textrm{To obtain a Software Engineer as Backend.}

\section*{Summary}

\textrm{Web developer specialist in backend development.}

\textrm{Experience developing large on-premise system for financial institutions using Java and Spring Boot.}

\textrm{And experience in microsevices development using Kotlin and Spring Boot, Vue.js, TypeScript for a recruitment web app.}

\textrm{I have worked in the IT industry for over 10 years and have experience in system design and operations.}

\textrm{I have participated in various projects in the IT industry for 4 years as a company employee and more than 7 years as a freelancer.}

\section*{Skills And Tools}

\textrm{\texttt{Java|Kotlin|PHP|Ruby|TypeScript|SQL|Spring Boot|Ruby on Rails|FuelPHP|Vue.js|Node.js|Nuxt.js}}
\textrm{\texttt{JUnit|Jest|Git|MySQL|Oracle|Docker|Swagger|GitHub|GitLab|Bitbucket|CircleCI|Jenkins|GCP|AWS}}

\section*{Work Experience}

\begin{itemize}
\item \textbf{Freelancer April 2015 - present, Tokyo, Remote work.}
    \begin{itemize}
        \item Recruitment Agency              : Full Stack Engineer, Domain-driven design, microsevices.
        \item Shopping Mall                   : Back End Engineer, MVC, Reactive Programming.
        \item Foreign Exchange Margin Trading : Full Stack Engineer, MVC, On-premises.
    \end{itemize}
\item \textbf{Corporate Employee April 2011 -  March 2015, Tokyo.}
    \begin{itemize}
        \item Credit Card     : Back End Engineer, MVC, On-premises.
        \item Debt Collection : Back End Engineer, MVC, On-premises.
        \item Syndicated Loan : Back End Engineer, MVC, On-premises.
    \end{itemize}
\end{itemize}

\section*{Education}

\textrm{TOKYO DENKI UNIVERSITY}

\textrm{Bachelor of Information, March 2011}

\section*{Self Taught}
\textrm{\texttt{Golang|Haskell|Scala|Python}}

\end{document}